---
title: "Problem Set 1"
author: "Santiago Taborga"
date: '2025-01-29'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  eval = TRUE,
  fig.align = 'center', 
  message = FALSE,
  warning = FALSE
)

library(tidyverse)
library(knitr)
library(haven)
library(Matrix)
library(lfe)
library(dplyr)
library(tidyr)

madagascar <- read_spss('Madagascar_Round9.sav') 

madagascar <-
  madagascar %>%
    select(DATEINTR, Q1, Q2, Q100, Q101, Q78A, Q78B) %>%
  mutate(Per = 1 / nrow(madagascar) *100)

```

1. I chose the country of Madagascar. There are 1200 respondents and the interviews were conducted between `r min(madagascar$DATEINTR)` and `r max(madagascar$DATEINTR)`.

2. Respondents have a broad set of backgrounds. There were a total of `r nrow(madagascar)` respondents. People's age ranges from `r min(madagascar$Q1)` to `r max(madagascar$Q1)` years old, with an mean age of `r round(mean(madagascar$Q1), 2)` and a median age of `r median(madagascar$Q1)`. There are `r sum(madagascar$Q100 == 1)` men and `r sum(madagascar$Q100 == 2)` women. `r round((sum(madagascar$Q2 == 420) / nrow(madagascar) * 100), 2)`% of people speak Malagasy officiel, `r round((sum(madagascar$Q2 == 421) / nrow(madagascar) * 100), 2)`% of people speak Malagasy avec spécificité régionale, and `r round((sum(madagascar$Q2 == 9995) / nrow(madagascar) * 100), 2)`% of people speak another language. `r round((sum(madagascar$Q101 == 1) / nrow(madagascar) * 100), 2)`% of people are Black/African, `r round((sum(madagascar$Q101 == 2) / nrow(madagascar) * 100), 2)`% of people are White/European, and `r round((sum(madagascar$Q101 == 3) / nrow(madagascar) *100), 2)`% of people are Coloured/Mixed Race.

```{r, fig.cap='Descriptive Stats'}
tab1 <- 
  madagascar %>%
  select(Q2, Q100, Q101, Per) %>%
  pivot_longer(cols = -Per) %>%
  group_by(name, value) %>%
  summarise(Percent = round(sum(Per), 2)) %>%
  mutate(name = case_when(name == "Q100" ~ "Gender",
                          name == "Q101" ~ "Race",
                          name == "Q2" ~ "Language"),
         value = case_when((name == "Gender" & value == 1) ~ "Men",
                           (name == "Gender" & value == 2) ~ "Women",
                           (name == "Race" & value == 1) ~ "Black/African",
                           (name == "Race" & value == 2) ~ "White/European",
                           (name == "Race" & value == 3) ~ "Coloured/Mixed Race",
                           (name == "Language" & value == 420) ~ "Malagasy officiel",
                           (name == "Language" & value == 421) ~ "Malagasy avec spécificité régionale",
                           (name == "Language" & value == 9995) ~ "Other"))
colnames(tab1)[which(names(tab1) == "value")] <- "Value" 
colnames(tab1)[which(names(tab1) == "name")] <- "Variable"

tab1 <- tab1 %>% kable(caption = "Descriptive Stats")
tab1
```

3. 
```{r, fig.cap='Political and Economic Influence: China'}
tab2 <- 
  madagascar %>%
  count(Q78A, name = "Number") %>%
  mutate(Percent = round((100 * Number/sum(Number)), 2),
         Q78A = case_when(Q78A == 1 ~ "Very negative",
                          Q78A == 2 ~ "Somewhat negative",
                          Q78A == 3 ~ "Neither positive nor negative",
                          Q78A == 4 ~ "Somewhat positive",
                          Q78A == 5 ~ "Very positive",
                          Q78A == 8 ~ "Refused",
                          Q78A == 9 ~ "Don't know",
                          Q78A == -1 ~ "Missing"))

colnames(tab2)[which(names(tab2) == "Q78A")] <- "Influence"

```
The economic and political influence of China in Madagascar is most often seen as "`r tab2$Influence[tab2$Percent == max(tab2$Percent)]`". The numbers show that `r tab2$Percent[tab2$Influence == "Very negative"]`% of people found it to be very negative, `r tab2$Percent[tab2$Influence == "Somewhat negative"]`% somewhat negative, `r tab2$Percent[tab2$Influence == "Neither positive nor negative"]`% neither positive nor negative, `r tab2$Percent[tab2$Influence == "Somewhat positive"]`% somewhat positive, and `r tab2$Percent[tab2$Influence == "Very positive"]`% very positive.

```{r, fig.cap='Table 2'}
tab2 <- kable(tab2, caption = "Political and Economic Influence: China")
tab2
```

4. 
```{r, fig.cap='Political and Economic Influence: United States'}
tab2 <- 
  madagascar %>%
  count(Q78B, name = "Number") %>%
  mutate(Percent = round((100 * Number/sum(Number)), 2),
         Q78B = case_when(Q78B == 1 ~ "Very negative",
                          Q78B == 2 ~ "Somewhat negative",
                          Q78B == 3 ~ "Neither positive nor negative",
                          Q78B == 4 ~ "Somewhat positive",
                          Q78B == 5 ~ "Very positive",
                          Q78B == 8 ~ "Refused",
                          Q78B == 9 ~ "Don't know",
                          Q78B == -1 ~ "Missing"))

colnames(tab2)[which(names(tab2) == "Q78B")] <- "Influence"

```
The economic and political influence of China in Madagascar is most often seen as "`r tab2$Influence[tab2$Percent == max(tab2$Percent)]`". The numbers show that `r tab2$Percent[tab2$Influence == "Very negative"]`% of people found it to be very negative, `r tab2$Percent[tab2$Influence == "Somewhat negative"]`% somewhat negative, `r tab2$Percent[tab2$Influence == "Neither positive nor negative"]`% neither positive nor negative, `r tab2$Percent[tab2$Influence == "Somewhat positive"]`% somewhat positive, and `r tab2$Percent[tab2$Influence == "Very positive"]`% very positive.

```{r, fig.cap='Table 3'}
tab2 <- kable(tab2, caption = "Political and Economic Influence: United States")
tab2
```

5. The t-test below is equal to -11.387. With 5% significance for a two-tailed t-test, I reject the null (|t| = 11.387 > 1.96). People view the economic and political influence of China significantly more negatively than the economic and political influence of the United States.

```{r, fig.cap="t-test"}
madagascar <-
  madagascar %>%
  mutate(
    across(
      Q78A:Q78B,
      ~ if_else(.x %in% 1:5, .x, NA)
      )
  )
t.test(madagascar$Q78A, madagascar$Q78B, paired = TRUE)
```
