---
title: "Problem Set 1"
author: "Santiago Taborga"
date: '2025-01-21'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  eval = TRUE,
  fig.align = 'center', 
  message = FALSE,
  warning = FALSE
)

library(tidyverse)
library(knitr)
library(haven)
library(Matrix)
library(lfe)
library(stargazer)

madagascar <- read_spss('Madagascar_Round9.sav')
```

1. I chose the country of Madagascar. There are 1200 respondents and the interviews were conducted between `r min(madagascar$DATEINTR)` and `r max(madagascar$DATEINTR)`.

2. Respondents have a broad set of backgrounds. People's age ranges from `r min(madagascar$Q1)` to `r max(madagascar$Q1)` years old, with an mean age of `r round(mean(madagascar$Q1), 2)` and a median age of `r median(madagascar$Q1)`. There are `r sum(madagascar$Q100 == 1)` men and `r sum(madagascar$Q100 == 2)` women. `r sum(madagascar$Q2 == 420)` people speak Malagasy officiel, `r sum(madagascar$Q2 == 421)` people speak Malagasy avec spécificité régionale, and `r sum(madagascar$Q2 == 9995)` speak another language.

```{r}

```

